---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# quickplot

<!-- badges: start -->
<!-- badges: end -->

The goal of quickplot is to produce a quick plot of two numerical vairables. The graph that is produced places the x parameter on the x-axis, and the y parameter on the y-axis. These variables are determined based on the dataframe that is defined as the data parameter.


## Installation

quickplot is not yet on CRAN. But, you can download it from this repository using the following R command:

``` r
devtools::install_github("Kyle-Amaral/quickplot")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(quickplot)
scatter_graph(palmerpenguins::penguins, bill_length_mm, flipper_length_mm)
```

This package is special because it produces a scatterplot that can be used to see preliminary trends between two numerical variables. All it requires is the dataframe and the two numerical variables of interest. It will also make sure that only numerical variables are being used and will let you know why the function is not working (ie. inputted a factor variable instead of numerical).

```{r}
library(quickplot)
scatter_graph(mtcars, mpg, hp)
```
